SunPy - Python for Solar Physics

### 2014-01-20 3-3-HELIO.tex
Fix merge related issues

The HELiophysics Integrated Observatory (HELIO)\footnote{\url{http://helio-vo.eu}} has put together a list of web services which allows the scientist to query them in order to discover data in the heliosphere (\eg, solar, planetary, inter-planetary data, \cdots)\citep{dps2012}. 
HELIO has been built with a Service-Oriented Architecture, 
\ie HELIO capabilities are split into a number of tasks that are implemented as separate services. 
HELIO counts with up to nine different public services, which allows to the scientist to look up in different catalogues of registered events, features on the sun and data from instruments in the heliosphere. 
Additionally, HELIO provides of a service that uses a propagation model to link the data in different points of the solar system by its original nature 
(\eg., Earth auroras are a signature of magnetic field disturbances produced few days before on the Sun).
The main interface to acccess to HELIO is through its front-end\footnote{
\url{http://hfe.helio-vo.eu}},
but since the system is based in webservices they can be accessed from many different tools.

>>>>

The HELiophysics Integrated Observatory 
(HELIO)\footnote{\url{http://helio-vo.eu}} has put together a list of web 
services which allows the scientist to query them in order to discover data in 
the heliosphere (\textit{e.g.}, solar, planetary, inter-planetary data, 
...)\cite{dps2012}. 
HELIO has been built with a Service-Oriented Architecture, 
\textit{i.e.} HELIO capabilities are split into a number of tasks that are 
implemented as separate services. 
HELIO counts with up to nine different public services, which allows to the scientist to look up in different catalogues of registered events, features on the sun and data from instruments in the heliosphere. 
Additionally, HELIO provides of a service that uses a propagation model to link the data in different points of the solar system by its original nature 
(\textit{e.g.}, Earth auroras are a signature of magnetic field disturbances 
produced few days before on the Sun).
The main interface to acccess to HELIO is through its front-end\footnote{
\url{http://hfe.helio-vo.eu}},
but since the system is based in webservices they can be accessed from many different tools.

### 2014-01-20 3-4-Helioviewer.tex
Fix merge related issues

# print a list of datasources and their associated ids
for observatory, instruments in datasources.items():
    for inst, detectors in instruments.items():
        for det, measurements in detectors.items():
            for meas, params in measurements.items():
                print("%s %s: %d" % (observatory, params['nickname'], params['sourceId']))
\caption{Initializing the Helioviewer client and listing the full
  range of image data available.}
\label{code:hv:datasources}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0, width=512, height=512)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304.eps}
\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image available at
  www.helioviewer.org.}
\label{code:hv:downloadlatestpng}
\end{listing}

@@

The Helioviewer API allows composition and overlay of images from
multiple sources, based on the positioning metadata in the source FITS
file.  SunPy accesses this overlay/composition capability through the
\texttt{download_png} method of the Helioviewer client.  Example
\ref{code:hv:overlaid} gives an example of the composition of three
separate images in to a single image.

>>>>

# print a list of datasources and their associated ids
for observatory, instruments in datasources.items():
    for inst, detectors in instruments.items():
        for det, measurements in detectors.items():
            for meas, params in measurements.items():
                print("%s %s: %d" % (observatory, params['nickname'], 
                %%%%params['sourceId']))
\end{minted}
\caption{Initializing the Helioviewer client and listing the full
  range of image data available.}
\label{code:hv:datasources}
\end{listing}

@@

\begin{listing}
\begin{minted}{python}
hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]", x0=0, y0=0, width=512, height=512)
\end{minted}
\includegraphics[width=0.8\columnwidth]{helioviewer_latest_aia_304.eps}
\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
available at \url{www.helioviewer.org}.}
\label{code:hv:downloadlatestpng}
\end{listing}

@@

The Helioviewer API allows composition and overlay of images from
multiple sources, based on the positioning metadata in the source FITS
file.  SunPy accesses this overlay/composition capability through the
\texttt{download\_png} method of the Helioviewer client.  Example
\ref{code:hv:overlaid} gives an example of the composition of three
separate images in to a single image.

### 2014-01-20 4-Util.tex
Fix merge related issues

\subsection{Coordinates}
Coordinate transformations are frequently a necessary task within the solar data analysis
workflow. Likely the most often used transformation is from observer coordinates (e.g. 
sky coordinates) to a coordinate system which is mapped onto the solar surface (e.g.
latitude and longitude). This transformation is necessary to compare the true physical
distance between different solar features. This type of transformation is not unique
to solar observations (e.g. planetary) but it is not provided by the Astropy coordinates 
package. The coordinates package implements the World Coordinate System (WCS) for solar
coordinates as described by \cite{Thompson2000}. The coordinate system transformations
currently implemented as those most useful for most solar data analysis, namely 
converting from Helioprojective-Cartesian (HPC) to Heliographic coordinates (HG). HPC 
which describes the positions on the Sun as angles measured from the center of the solar 
disk (usually in arcseconds) using cartesian coordinates (X, Y) This is the coordinates 
most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). HG
coordinates express positions on the Sun using longitude and latitude on the solar 
sphere. There are two standards for this coordinate system, Stonyhurst-Heliographic 
where the origin is at the intersection of the solar equator and 
the central meridian as seen from Earth and Carrington-Heliographic is a system which is
fixed to the Sun and does not depend on Earth. The implementation of these transformations
pass through common coordinate system called Heliocentric-Cartesian (HCC) where positions 
are expressed in true (deprojected) physical distances instead of angles on the celestial sphere.
These transformations require some knowledge of the location of the observer which is
usually provided by the image header information. In case where it is not, the observer
is assumed to be at Earth.

@@

\subsubsection{constants}
The purpose of the constants package is to provide a number of solar-related constants 
in order to provide consistency in the calculations of derived solar values both within the
SunPy code base but also to the user. Every solar constants is provided as a Constant objects as defined by Astropy. 
Each Constant object defines a Quantity, a number associated with a unit, along with the constant's provenance
(i.e. reference) as well as its uncertainty. Using Astropy's Quantities, any solar constant
can easily be converted between different units as can be seen in Figure~\ref{fig:constants_code} as well
as between SI or cgs with a single command.  As these objects inherit from Numpy's ndarray,
they work well with standard representations of numbers.
For convenience a number shortcuts to frequently used constants are provided directly when importing
the sub-package. A larger list of constants can be accessed through an interface modelled 
on that provided by the SciPy constants package and are available as a dictionary called
physical_constants. To view all quickly a print_all() function is available.

>>>>

\subsection{Coordinates}
Coordinate transformations are frequently a necessary task within the solar 
data analysis workflow. Likely the most often used transformation is from 
observer coordinates (e.g. sky coordinates) to a coordinate system which is 
mapped onto the solar surface (e.g. latitude and longitude). This 
transformation is necessary to compare the true physical distance between 
different solar features. This type of transformation is not unique
to solar observations (e.g. planetary) but it is not provided by the Astropy 
coordinates package. The coordinates package implements the World Coordinate 
System (WCS) for solarcoordinates as described by \cite{Thompson2000}. The 
coordinate system transformations currently implemented as those most useful 
for most solar data analysis, namely converting from Helioprojective-Cartesian 
(HPC) to Heliographic coordinates (HG). HPC which describes the positions on 
the Sun as angles measured from the center of the solar disk (usually in 
arcseconds) using cartesian coordinates (X, Y) This is the coordinates 
most often defined in solar image data (e.g. SDO/AIA images, SOHO/EIT, TRACE). 
HG coordinates express positions on the Sun using longitude and latitude on 
the 
solar sphere. There are two standards for this coordinate system, 
Stonyhurst-Heliographic where the origin is at the intersection of the solar 
equator and the central meridian as seen from Earth and 
Carrington-Heliographic 
is a system which is fixed to the Sun and does not depend on Earth. The 
implementation of these transformations pass through common coordinate system 
called Heliocentric-Cartesian (HCC) where positions are expressed in true 
(deprojected) physical distances instead of angles on the celestial sphere.
These transformations require some knowledge of the location of the observer 
which is usually provided by the image header information. In case where it is 
not, the observer is assumed to be at Earth.

@@

\subsubsection{constants}
The purpose of the constants package is to provide a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values both within the SunPy code base but also to the user. Every solar 
constants is provided as a Constant objects as defined by Astropy. Each 
Constant object defines a Quantity, a number associated with a unit, along with 
the constant's provenance (i.e. reference) as well as its uncertainty. Using 
Astropy's Quantities, any solar constant can easily be converted between 
different units as can be seen in Figure~\ref{fig:constants_code} as well
as between SI or cgs with a single command.  As these objects inherit from 
Numpy's ndarray, they work well with standard representations of numbers.
For convenience a number shortcuts to frequently used constants are provided 
directly when importing the sub-package. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and are available as a dictionary called \texttt{physical\_constants}. 
To view all quickly a \texttt{print\_all()} function is available.
